Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-15 illustrate.tex
updates

\subsection{Illustrative Examples}
In this section, we present some illustrative examples and make some useful remarks about the same.
\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix},0<\epsilon<0.1$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.
\end{example}
The above example \Cref{ex:pdas} illustrates the use of appropriate $U_i,i=1,2,3$ matrices to transform Hurwitz problems into positive definite problems. In particular, problem $P^2$ involves the use of a complex matrix $U_2$.
\begin{example}\label{ex:geo}
Consider the one dimensional case where $A_t=\rho$ for some $0<\rho<1$, $b_t$ a bounded $i.i.d$ zero mean random variable with variance $\sigma^2$, and $\ts=0$. We know that $e_t=(1-\alpha\rho)^t e_0+\sum_{s=1}^t (1-\alpha \rho)^{t-s}\alpha b_s$ and the MSE is given by
\begin{align*}
\EE{\norm{\thh_t}^2}&=\frac{1}{(t+1)^2}\left( (\alpha\rho)^{-1}(1-\alpha\rho)^{t+1}) \theta_0+ \sum_{s=1}^t (\alpha\rho)^{-1}(1-\alpha \rho)^{t-s+1} \alpha b_s\right)^2\\
&\leq (\alpha\rho)^{-2}\left(\frac{\norm{\theta_0}^2}{t^2}+\frac{\alpha^2\sigma^2}{t}\right)
\end{align*}
\end{example}
The above example helps to interpret the error dynamics of \Cref{eq:lsa} in terms of sum of a geometric series with common factor $\alpha\rho$.
\begin{example}
Consider deterministic problems $P^1$, $P^2$ and $P^3$ with $A_{P^1}=\begin{bmatrix} 10 &100\\ 0 &10\end{bmatrix}$, $A_{P^2}=\begin{bmatrix} 10 &9.99\\ 0 &10\end{bmatrix}$, $A_{P^3}=\begin{bmatrix} 10 &0 \\ 0 &10\end{bmatrix}$, $\sigma^2_{A_{P^i}}=\sigma_{b_{P^i}}=0,\,i=1,2,3$. Note that $P^1$, $P^2$ and $P^3$ are respectively H, PD, SPD respectively.
\end{example}
\begin{comment}
We now list the following observations:
\begin{itemize}%[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item In all the three instance, $0<\alpha<\frac2{10}$ ensures that the error $\norm{\eh_t}\ra 0$ as $t\ra\infty$. Thus the range of $\alpha$ is uniform across $P^i,i=1,2,3$.
\item $\rhos{P^1}=\rhod{P^1}<0$, and hence one cannot apply results of \Cref{th:pdrate}. However, with  $U=\begin{bmatrix}1 &0 \\ 0 &0.2-\epsilon\end{bmatrix}$ for some $\epsilon>0$ we have $P^1_U$ to be the distribution concentrated on the matrix $A_{P^1_U}=\begin{bmatrix} 10 &20 \\ 0 &10\end{bmatrix}$ and one can apply the results of \Cref{thm:simtran,cor:as}. Notice that the condition number $\norm{U}{U^-1}\approx 5$.
\end{itemize}
\end{comment}
\input{plts}

>>>>

\subsection{Illustrative Examples}
In this section, we present some illustrative examples and make some useful remarks about the same.
\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix},0<\epsilon<0.1$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.
\end{example}
The above example \Cref{ex:pdas} illustrates the use of appropriate $U_i,i=1,2,3$ matrices to transform Hurwitz problems into positive definite problems. In particular, problem $P^2$ involves the use of a complex matrix $U_2$.
\begin{example}\label{ex:geo}
Consider the one dimensional case where $A_t=\rho$ for some $0<\rho<1$, $b_t$ a bounded $i.i.d$ zero mean random variable with variance $\sigma^2$, and $\ts=0$. We know that $e_t=(1-\alpha\rho)^t e_0+\sum_{s=1}^t (1-\alpha \rho)^{t-s}\alpha b_s$ and the MSE is given by
\begin{align*}
\EE{\norm{\thh_t}^2}&=\frac{1}{(t+1)^2}\left( (\alpha\rho)^{-1}(1-\alpha\rho)^{t+1}) \theta_0+ \sum_{s=1}^t (\alpha\rho)^{-1}(1-\alpha \rho)^{t-s+1} \alpha b_s\right)^2\\
&\leq (\alpha\rho)^{-2}\left(\frac{\norm{\theta_0}^2}{t^2}+\frac{\alpha^2\sigma^2}{t}\right)
\end{align*}
\end{example}
The above example helps to interpret the error dynamics of \Cref{eq:lsa} in terms of sum of a geometric series with common factor $\alpha\rho$.
\begin{comment}
\begin{example}
Consider deterministic problems $P^1$, $P^2$ and $P^3$ with $A_{P^1}=\begin{bmatrix} 10 &100\\ 0 &10\end{bmatrix}$, $A_{P^2}=\begin{bmatrix} 10 &9.99\\ 0 &10\end{bmatrix}$, $A_{P^3}=\begin{bmatrix} 10 &0 \\ 0 &10\end{bmatrix}$, $\sigma^2_{A_{P^i}}=\sigma_{b_{P^i}}=0,\,i=1,2,3$. Note that $P^1$, $P^2$ and $P^3$ are respectively H, PD, SPD respectively.
\end{example}
\input{plts}
\end{comment}

### 2017-05-15 instance.tex
updates

\section{Main Results}\label{sec:mainresults}
In this section, we derive instance dependent bounds  which is valid for a fixed $P$ and in the \Cref{sec:uniform}, address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions over $\C^{\dcd}$. Here, we only present the results followed by a discussion and the detailed proofs can be found in \Cref{sec:appendix}.
\begin{lemma}\label{lm:pd}
Let $P$ be positive definite, then there exists an $\alpha_P>0$ and $U\in \gln$ such that $\rhod{P_U}>0$ and $\rhos{P_U}>0,~\forall \alpha \in (0,\alpha_P)$.
\end{lemma}
\begin{lemma}\label{lm:simtran}[Similarity Transformation]
Let $P$ be Hurwitz, then there exists a $U\in \gln$ such that $P_U$ is positive definite.
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}

@@

\item \textbf{Role of $U$:} When the given problem $P$ is positive definite, it is straighforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$. However, the problem $P$ being Hurwitz does not guarantee positive definiteness (see \Cref{ex:pdas}). This can be remedied by a similiarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. To see this, let $\gamma_t\eqdef U^{-1 }\theta_t$ be a basis transformation, and let us re-write \eqref{conststep} in $\gamma_t$ by pre-multiplying \eqref{constste[} by $U^{-1}$ as shown below:

@@

This completes the transformation of a Hurwirz problem $P$ to a positive definite problem $P_U$. One can revert to $\theta_t$ by using $\theta_t=U\gamma_t$, and this explains the reason for the condition number $\cond{U}$ in \Cref{th:rate}. We would like to add that when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. We would like to mention that such similarity transformations have been in the past for analyzing LSA algorithms in RL \cite{lihong} (see \Cref{sec:related} for more details).

@@

From \eqref{errec} it is clear that the error dynamics depends on the $i)$ properties of the random matrix, $ii)$ properties of the noise. In the absence of the noise term in \eqref{eq:errec}, we have $e_t=(I-\alpha A_t) e_{t-1}=\Pi_{s=1}(I-\alpha A_s) e_0$, i.e., the inital error is get multiplied by a product of random matrices. In such a scenario, we can guess that whether or not the algorithm forgets the bias $\norm{\theta_0-\ts}$, depends on whether the matrix product is contracting. One way to characterize this contracting property is to look at the spectral radius of the random matrix, which is given by

@@

\item \textbf{Behaviour for extreme value of $\alpha$:} For smaller values of stepsize, i.e., $\alpha\approx 0$, the bias term blows up, due to the presence of $\alpha^{-1}$ term. This is due to the fact that the stepsizes determine the learning rate and for smaller stepsizes the learning rate is slower. However, in this case the noise term does not blow up, a fact that can appreciated by looking at \Cref{th:rate} where $\alpha$ is seen to multiply the variances $\sigma^2_P$ and $\sigma^2_b$. In quantitative terms, we can see that the $\alpha^{-2}$ and $\alpha^2$ terms can each other. For larger values of $\alpha$ i.e., $\alpha\ra \alpha_{P}$ (or $\alpha_{P_U}$ as the case may be), the bounds blow up again, due to the fact that $\rhos{P}\ra 0$ in this case.
\item \textbf{Lower Bound} in \Cref{th:lb} shows that

>>>>

\section{Main Results}\label{sec:mainresults}
In this section, we derive instance dependent bounds that are valid for a given problem $P$ (satisfying \Cref{assmp:lsa}) and in the \Cref{sec:uniform}, address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions (problems). Here, we only present the main results followed by a discussion and the detailed proofs can be found in \Cref{sec:appendix}.
\begin{lemma}\label{lm:pd}
Let $P$ be positive definite, then there exists an $\alpha_P>0$ and $U\in \gln$ such that $\rhod{P_U}>0$ and $\rhos{P_U}>0,~\forall \alpha \in (0,\alpha_P)$.
\end{lemma}
\begin{lemma}\label{lm:simtran}[Similarity Transformation]
Let $P$ be Hurwitz, then there exists a $U\in \gln$ such that $P_U$ is positive definite.
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}

@@

\item \textbf{Role of $U$:} When the given problem $P$ is positive definite, it is straightforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$. However, the problem $P$ being Hurwitz does not guarantee positive definiteness (see \Cref{ex:pdas}). This can be remedied by a similarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. To see this, let $\gamma_t\eqdef U^{-1 }\theta_t$ be a basis transformation, and let us re-write \eqref{conststep} in $\gamma_t$ by pre-multiplying \eqref{constste[} by $U^{-1}$ as shown below:

@@

This completes the transformation of a Hurwitz problem $P$ to a positive definite problem $P_U$. One can revert to $\theta_t$ by using $\theta_t=U\gamma_t$, and this explains the reason for the condition number $\cond{U}$ in \Cref{th:rate}. We would like to add that when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. We would like to mention that such similarity transformations have been in the past for analyzing LSA algorithms in RL \cite{lihong} (see \Cref{sec:related} for more details).

@@

From \eqref{errec} it is clear that the error dynamics depends on the $i)$ properties of the random matrix, $ii)$ properties of the noise. In the absence of the noise term in \eqref{eq:errec}, we have $e_t=(I-\alpha A_t) e_{t-1}=\Pi_{s=1}(I-\alpha A_s) e_0$, i.e., the initial error is get multiplied by a product of random matrices. In such a scenario, we can guess that whether or not the algorithm forgets the bias $\norm{\theta_0-\ts}$, depends on whether the matrix product is contracting. One way to characterize this contracting property is to look at the spectral radius of the random matrix, which is given by

@@

\item \textbf{Behaviour for extreme value of $\alpha$:} For smaller values of step-size, i.e., $\alpha\approx 0$, the bias term blows up, due to the presence of $\alpha^{-1}$ term. This is due to the fact that the stepsizes determine the learning rate and for smaller stepsizes the learning rate is slower. However, in this case the noise term does not blow up, a fact that can appreciated by looking at \Cref{th:rate} where $\alpha$ is seen to multiply the variances $\sigma^2_P$ and $\sigma^2_b$. In quantitative terms, we can see that the $\alpha^{-2}$ and $\alpha^2$ terms can each other. For larger values of $\alpha$ i.e., $\alpha\ra \alpha_{P}$ (or $\alpha_{P_U}$ as the case may be), the bounds blow up again, due to the fact that $\rhos{P}\ra 0$ in this case.
\item \textbf{Lower Bound} in \Cref{th:lb} shows that the factor $\rhos{P}\rhod{P}$ appearing in the upper bound in \Cref{th:rate} is inevitable for general LSA with CS-PR. However, there are specific examples such as SGD for the linear regression problem considered by \citet{bach} where this factor can be avoided (for further remarks see \Cref{sec:related}).

### 2017-05-15 not.tex
updates

 %Also, by $A_{ij}$ we denote the entry of matrix $A$ in the $i^{th}$ row and $j^{th}$ column.
We use $\R^{\dcd}$ and $\C^{\dcd}$ to denote $\dcd$ matrices with real and complex entries respectively. The notation for (conjugage) transpose carries over from vectors.
The norm of the matrix $A$ in given by $\norm{A}\eqdef \sup_{x\in \C^d:\norm{x}=1} \norm{Ax}$. For any $x\in\C^d$, we denote the general quadratic norm with respect to a hermitian matrix $C$ by $\norm{x}^2_C\eqdef x^*\, C \,x$. We use $\cond{A}=\norm{A}\norm{A^{-1}}$ to denote the condition number of the matrix $A$. We denote the identity matrix in $\C^{\dcd}$ by $\I$ and the set of invertible $\dcd$ complex matrices by $\gln$.
\begin{comment}
We use $A\succeq 0$ to denote that the
square matrix $A$ is hermitian and positive semidefinite (HPD):
$A = A^*$, $\inf_x x^* A x\ge 0$.
For $A,B$ HPD matrices, $A\succeq B$ holds if $A-B\succeq 0$.
We also use $A\succ B$ similarly to denote that $A-B \succ 0$.
We also use $\preceq$ and $\prec$ analogously.
\end{comment}
For a positive real number $B>0$, we denote by $\C^{d}_B=\{b\in \C^d\mid \norm{b}\leq B\}$ and by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \norm{A}\leq B\}$ the set of complex vectors and matrices whose norms are bounded $B$.
%We denote by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$ and  $\R^{\dcd}_B=\{A\in \R^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$.
%We use $\P$ to denote the set of probability distribution over $\C^{\dcd}$.
%We denote the set of distributions over $\C_B^{\dcd}$ by $\P$.
Let $P$ be a distribution over $C^{\dcd}$, we use $A\sim P$ to denote $A$ is distributed according to $P$. For $U\in \gln$, we denote by $P_U$ the distribution of $U^{-1}\,A\,U$, where $A\sim P$. $\E$ denotes mathematical expectation.
\begin{comment}
 We use $A\sim P$ to denote the fact that the random variable $A$ is distributed according to distribution $P$. Let the random matrix $A\sim P$, and $U\in \gln$, we use $P_U$ to denote the distribution of the random matrix $U^{-1}A U$.
\end{comment}
\begin{definition}\label{def:dist}
Let $P=(P^V,P^M)$ denote a $2$-tuple of probability distributions; $P^V$ over $\C^{d}$ and $P^M$ over $\C^{\dcd}$. Define
\begin{align*}
A_P&=\int M dP^M(M),\quad C_P=\int M^* M dP^M(M), \quad b_P=\int V dP^V(V)\\
\rhod{P}&\eqdef {\inf}_{x\in\C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha A_P^* A_P\right)x},\\ \rhos{P}&\eqdef{\inf}_{x\in \C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha C_P\right)x}
\end{align*}
\end{definition}
Note that $\rhod{P}>\rhos{P}$.
\begin{definition}\label{def:simdist}
Let $P=(P^V,P^M)$ as in \Cref{def:dist}; $b\sim P^V$ and $A\sim \P^M$ be random variables distributed according to $P^V$ and $P^M$. For $U\in \gln$ define $P_U=(P_U^V,P_U^M)$ to be the distributions of $U^{-1}b$ and $U^{-1}AU$.
\end{definition}
\begin{definition}
We call a matix $A\in \C^{\dcd}$ to be \emph{Hurwitz} (H) if all eigenvalues of $A$ have positive real parts. We call a matrix $A\in \C^{\dcd}$ to be \emph{Positive Definite} (PD) if $\ip{x,Ax} >0,\,\forall x\neq 0 \in \C^{d}$.  We call a matrix $A\in \C^{\dcd}$ to be \emph{Symmetric Positive Definite} (SPD) is it is symmetric i.e., $A^\top=A$ and PD.
\end{definition}
\begin{definition}\label{distpd}
We call a distribution $P$ to be H/PD/SPD if $A_P$ is H/PD/SPD.
\end{definition}
\begin{example}
The matrices $\begin{bmatrix}0.1 &-1\\ 1 & 0.1\end{bmatrix}$, $\begin{bmatrix} 0.1 & 0.1 \\ 0 & 0.1\end{bmatrix}$ and $\begin{bmatrix}0.1 &0 \\ 0 & 0.1\end{bmatrix}$ are examples of H, PD and SPD respectively.
\end{example}

>>>>

 %Also, by $A_{ij}$ we denote the entry of matrix $A$ in the $i^{th}$ row and $j^{th}$ column.
We use $\R^{\dcd}$ and $\C^{\dcd}$ to denote $\dcd$ matrices with real and complex entries respectively. The notation for (conjugate) transpose carries over from vectors.
The norm of the matrix $A$ in given by $\norm{A}\eqdef \sup_{x\in \C^d:\norm{x}=1} \norm{Ax}$. For any $x\in\C^d$, we denote the general quadratic norm with respect to a hermitian matrix $C$ by $\norm{x}^2_C\eqdef x^*\, C \,x$. We use $\cond{A}=\norm{A}\norm{A^{-1}}$ to denote the condition number of the matrix $A$. We denote the identity matrix in $\C^{\dcd}$ by $\I$ and the set of invertible $\dcd$ complex matrices by $\gln$.
\begin{comment}
We use $A\succeq 0$ to denote that the
square matrix $A$ is hermitian and positive semidefinite (HPD):
$A = A^*$, $\inf_x x^* A x\ge 0$.
For $A,B$ HPD matrices, $A\succeq B$ holds if $A-B\succeq 0$.
We also use $A\succ B$ similarly to denote that $A-B \succ 0$.
We also use $\preceq$ and $\prec$ analogously.
\end{comment}
For a positive real number $B>0$, we denote by $\C^{d}_B=\{b\in \C^d\mid \norm{b}\leq B\}$ and by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \norm{A}\leq B\}$ the set of complex vectors and matrices whose norms are bounded $B$.
%We denote by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$ and  $\R^{\dcd}_B=\{A\in \R^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$.
%We use $\P$ to denote the set of probability distribution over $\C^{\dcd}$.
%We denote the set of distributions over $\C_B^{\dcd}$ by $\P$.
Let $P$ be a distribution over $C^{\dcd}$, we use $A\sim P$ to denote $A$ is distributed according to $P$. For $U\in \gln$, we denote by $P_U$ the distribution of $U^{-1}\,A\,U$, where $A\sim P$. $\E$ denotes mathematical expectation.
\begin{comment}
 We use $A\sim P$ to denote the fact that the random variable $A$ is distributed according to distribution $P$. Let the random matrix $A\sim P$, and $U\in \gln$, we use $P_U$ to denote the distribution of the random matrix $U^{-1}A U$.
\end{comment}
\begin{definition}\label{def:dist}
Let $P=(P^V,P^M)$ denote a $2$-tuple of probability distributions; $P^V$ over $\C^{d}$ and $P^M$ over $\C^{\dcd}$. Define
\begin{align*}
A_P&=\int M dP^M(M),\quad C_P=\int M^* M dP^M(M), \quad b_P=\int V dP^V(V)\\
\rhod{P}&\eqdef {\inf}_{x\in\C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha A_P^* A_P\right)x},\\ \rhos{P}&\eqdef{\inf}_{x\in \C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha C_P\right)x}
\end{align*}
\end{definition}
Note that $\rhod{P}>\rhos{P}$.
\begin{definition}\label{def:simdist}
Let $P=(P^V,P^M)$ as in \Cref{def:dist}; $b\sim P^V$ and $A\sim \P^M$ be random variables distributed according to $P^V$ and $P^M$. For $U\in \gln$ define $P_U=(P_U^V,P_U^M)$ to be the distributions of $U^{-1}b$ and $U^{-1}AU$.
\end{definition}
\begin{definition}
We call a matrix $A\in \C^{\dcd}$ to be \emph{Hurwitz} (H) if all eigenvalues of $A$ have positive real parts. We call a matrix $A\in \C^{\dcd}$ to be \emph{Positive Definite} (PD) if $\ip{x,Ax} >0,\,\forall x\neq 0 \in \C^{d}$.  We call a matrix $A\in \C^{\dcd}$ to be \emph{Symmetric Positive Definite} (SPD) is it is symmetric i.e., $A^\top=A$ and PD.
\end{definition}
\begin{definition}\label{distpd}
We call a distribution $P$ to be H/PD/SPD if $A_P$ is H/PD/SPD.
\end{definition}
\begin{example}
The matrices $\begin{bmatrix}0.1 &-1\\ 1 & 0.1\end{bmatrix}$, $\begin{bmatrix} 0.1 & 0.1 \\ 0 & 0.1\end{bmatrix}$ and $\begin{bmatrix}0.1 &0 \\ 0 & 0.1\end{bmatrix}$ are examples of H, PD and SPD respectively.
\end{example}

### 2017-05-15 prob.tex
updates

can then be implemented in $O(d)$ time and $O(d)$ storage, which makes the algorithm particularly attractive in large-scale computations when $n$ is in the range of thousands or more.\par

@@

\item The baias $\norm{\theta_0-\ts}$ due to the initial condition $\theta_0$.

@@

Most resutls in the past including those that of \cite{bach} consider an SGD algorithm for quadratic loss minimization, where the matrix $A_P$ is SPD and the noise has additional strucutral properties (we discuss this briefly in \Cref{sec:lp}). As it turns out these nice properties are lost when $A_P$ is AS or PD (a property that is holds in RL settings). While from the standpoint of the tools and techniques used, we use techniques much similar to \cite{bach}, however, as mentioned, the fact that we no longer are dealing with gradient systems (that involve to SPD matrices) but general vector fields (that involve AS or PD matrices), poses important challenges.

@@

\todoch{Mention impotance of forgetting the bias etc. Mention that we really don't have control over $\norm{U}$}

>>>>

can then be implemented in $O(d)$ time and $O(d)$ storage, which makes the algorithm particularly attractive in large-scale computations when $d$ is in the range of thousands or more.\par

@@

\item The bias $\norm{\theta_0-\ts}$ due to the initial condition $\theta_0$.

@@

Most results in the past including those that of \cite{bach} consider an SGD algorithm for quadratic loss minimization, where the matrix $A_P$ is SPD and the noise has additional structural properties (we discuss this briefly in \Cref{sec:lp}). As it turns out these nice properties are lost when $A_P$ is AS or PD (a property that is holds in RL settings). While from the standpoint of the tools and techniques used, we use techniques much similar to \cite{bach}, however, as mentioned, the fact that we no longer are dealing with gradient systems (that involve to SPD matrices) but general vector fields (that involve AS or PD matrices), poses important challenges.

@@

\todoch{Mention importance of forgetting the bias etc. Mention that we really don't have control over $\norm{U}$}
